---
title: "FDA approved/Registerd Catheter, Intravascular Occluding Devices V1"
author: "Aswin Kithalawaarachchi"
date: "2023-08-16"
output:
  html_document:
    code_folding: hide
---

```{r warning=FALSE}
library("tidyverse")
library("kableExtra")
library("ggplot2")
library("lubridate")
```


Data was obtained from the FDA databse and Filterd under the CODE MJN(Catheter, Intravascular Occluding, Temporary)

```{r include=FALSE}
data <- read.csv("Data/FDA-MJN/device.txt", header = TRUE, sep = "|")
head(data,1)

```


## Names of all the companies that make these devices

```{r}
companies <- data %>% select(companyName) %>% distinct()
companies %>% kable()
```





## Different brands of deviced by company name

```{r}
brands <- data %>%  group_by(companyName) %>% select(brandName,companyName) %>% distinct()
brands %>% kable()
```

## Visualisation of Different brands by company with the distribution status

```{r Message=FALSE}


# Summarize data
brand_counts <- data %>%
  group_by(companyName, deviceCommDistributionStatus) %>%
  summarise(unique_brands = n_distinct(brandName)) %>%
  arrange(companyName, -unique_brands)

# Plot bar chart
ggplot(brand_counts, aes(x = reorder(companyName, -unique_brands), y = unique_brands, fill = deviceCommDistributionStatus)) +
  geom_col(position = "dodge") +
  labs(title = "Number of Unique Brands per Company", x = "Company", y = "Number of Unique Brands") +
  coord_flip() +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(fill = guide_legend(title = NULL))


```



##  Times takes for a device to come to the public after being registred 




accordingly on avarage it takes about 1052 days/2.88 years for a device to be registerd and be ready for the public 


# From this point onwards the data is filterd to only include REBOA devices 





```{r}
reboa_df <- read_csv("Data/reboa_filter.csv")

joined_df <- data %>% 
  inner_join(reboa_df, by = c("brandName" = "device name"))

```
```{r}
brands_filterd <- joined_df %>%  group_by(companyName) %>% select(brandName,companyName) %>% distinct()
brands_filterd %>% kable()
```

```{r}

# Summarize data
brand_counts <- joined_df %>%
  group_by(companyName, deviceCommDistributionStatus) %>%
  summarise(unique_brands = n_distinct(brandName)) %>%
  arrange(companyName, -unique_brands)

# Plot bar chart
ggplot(brand_counts, aes(x = reorder(companyName, -unique_brands), y = unique_brands, fill = deviceCommDistributionStatus)) +
  geom_col(position = "dodge") +
  labs(title = "Number of Unique REBOA Brands per Company", x = "Company", y = "Number of Unique Brands") +
  coord_flip() +
  theme_minimal() +
  theme(legend.position = "bottom") +
  guides(fill = guide_legend(title = NULL))

```

```{r}
joined_df %>%
  ggplot(aes(x = deviceCommDistributionStatus)) +
  geom_bar() +
  theme_minimal() +
  labs(title = "Distribution of Device Commercial Distribution Status",
       x = "Distribution Status",
       y = "Count")
```




```{r}
# Bar chart of version statuses
joined_df %>%
  ggplot(aes(x = publicVersionStatus)) +
  geom_bar() +
  theme_minimal() +
  labs(title = "Distribution of Public Version Statuses",
       x = "Version Status",
       y = "Count")


```

this graph says how many devices have undergone updates and how many have not 





